19th International Satisfiability Modulo Theories Competition (SMT-COMP 2024): Rules and Procedures

### 2024-05-07 rules/rules24.tex
Changed date in the rules for taking the opening value of the NYSE Composite Index.
Update Disclosure for M. Jonáš.

\begin{description}
\item[April~13] Deadline for new benchmark contributions.
\item[May~11] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~27] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~8] Deadline for final versions of solvers, including
  system descriptions.
\item[June~11] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[July~22-23] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

\header{Disclosure.}
Fran\c{c}ois Bobot is part of the developing team of the SMT solver COLIBRI~\cite{colibri}.
%
Martin Bromberger is part of the developing team of the SMT solver
SPASS-SATT~\cite{spass-satt}.
%
Martin Jon\'{a}\v{s} is part of the developing team of \todo{Martin J. please fill this out}.

>>>>

\begin{description}
\item[April~13] Deadline for new benchmark contributions.
\item[May~11] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~27] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~8] Deadline for final versions of solvers, including
  system descriptions.
\item[June~10] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[July~22-23] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

\header{Disclosure.}
Fran\c{c}ois Bobot is part of the developing team of the SMT solver COLIBRI~\cite{colibri}.
%
Martin Bromberger is part of the developing team of the SMT solver
SPASS-SATT~\cite{spass-satt}.
%
Martin Jon\'{a}\v{s} is part of the developing team of the SMT solver Q3B~\cite{Q3B} and was a member of the developing team of the SMT solver MathSAT5~\cite{MathSAT5}.
